Fig5

### 2020-03-07 analysis/figure5-maniptsne.Rmd
better colors and illustration

bcd <- plot_grid(b,c,d, nrow = 3, labels = c("b", "c", "d"), label_size = 8, rel_heights = c(1,1,1))

e <- plottsneelipsev2(hyptsne, hyptsne$hiloPRL, allcolors ) + labs(subtitle = "hypothalamus ~ estimated prolactin", x = NULL) + facet_wrap(~sex, scales = "free")  
f <- plottsneelipsev2(pittsne, pittsne$hiloPRL, allcolors ) + labs(subtitle = "pituitary ~ estimated prolactin", x = NULL) + facet_wrap(~sex, scales = "free")   
g <- plottsneelipsev2(gontsne, gontsne$hiloPRL, allcolors ) + labs(subtitle = "gonads ~ estimated prolactin" ) + facet_wrap(~sex, scales = "free")

efg <- plot_grid(e,f,g, nrow = 3, labels = c("h", "i", "j"), label_size = 8, rel_heights = c(1,1,1))

@@

hij <- plot_grid(h,i,j, nrow = 3, labels = c("e", "f", "g"), label_size = 8, rel_heights = c(1,1,1))

@@

fig6 <- plot_grid(expdesign2, bcdhijefg, nrow = 2, labels = c("e"), label_size = 8, rel_heights = c(0.5,1))
fig6

>>>>

bcd <- plot_grid(b,c,d, nrow = 3, labels = c("b"), label_size = 8, rel_heights = c(1,1,1))

e <- plottsneelipsev2(hyptsne, hyptsne$hiloPRL, allcolors ) + labs(subtitle = "hypothalamus ~ internal physiology", x = NULL) + facet_wrap(~sex, scales = "free")  
f <- plottsneelipsev2(pittsne, pittsne$hiloPRL, allcolors ) + labs(subtitle = "pituitary ~ internal physiology", x = NULL) + facet_wrap(~sex, scales = "free")   
g <- plottsneelipsev2(gontsne, gontsne$hiloPRL, allcolors ) + labs(subtitle = "gonads ~ internal physiology" ) + facet_wrap(~sex, scales = "free")

efg <- plot_grid(e,f,g, nrow = 3, labels = c("d"), label_size = 8, rel_heights = c(1,1,1))

@@

hij <- plot_grid(h,i,j, nrow = 3, labels = c("c"), label_size = 8, rel_heights = c(1,1,1))

@@

fig6 <- plot_grid(expdesign2, bcdhijefg, nrow = 2, labels = c("a"), label_size = 8, rel_heights = c(0.4,1))
fig6
